Model LF

### 2022-10-30 Final test.Rmd
Commit

COMMENT> ur equation slettet
IDENTITY> ur_test
EQ> ur_test = unemp/lf

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  yk_l_ds = TIMESERIES(c(yk_l_ds),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$ur = ur

@@

wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds
yk_l_ds_00 = S_model$simulation$yk_l_ds

@@

plot(yk_l_ds_00, col= "green"); lines(yk_l_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation

yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prod_bs1 = Shock_bs1$simulation$prod

@@

```{r}
plot(part_bs1, col= "green"); lines(part, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio

nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

## Hvorfor forskel?

```{r}
plot(ur_test_bs7b, col= "red"); lines(ur_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds

tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

@@

plot(unemp_000, col= "red"); lines(unemp_bs1, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(prod_01, col= "red"); lines(prod_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp

part_07b = Shock_7b$simulation$part
```

>>>>

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$ur = ur

@@

wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds

@@

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prod_bs1 = Shock_bs1$simulation$prod

@@

```{r}
plot(lf_bs1, col= "green"); lines(LF, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

@@

```{r}
###Gengivelse af stød til model
part_000 = Shock_0$simulation$part
unemp_000 = Shock_0$simulation$unemp
komp_r_000 = Shock_0$simulation$komp_r
part_000 = Shock_0$simulation$part
yk_ds_000 = Shock_0$simulation$yk_ds
pc_ds_000 = Shock_0$simulation$pc_ds
wage_ds_t_000 = Shock_0$simulation$wage_ds_t
ur_ds_000 = Shock_0$simulation$ur_ds
emp_000 = Shock_0$simulation$emp
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
lf_000 = Shock_0$simulation$lf
tilpas_pr_000 = Shock_0$simulation$tilpas_pr
u_ds_000 = Shock_0$simulation$u_ds
part_000 = Shock_0$simulation$part
nben_h_000 = Shock_0$simulation$nben_h
wage_ds_000 = Shock_0$simulation$wage_ds
dp_person_000 = Shock_0$simulation$dp_person
kont_h_ratio_000 = Shock_0$simulation$kont_h_ratio

@@

plot(lf_000, col= "red"); lines(lf_bs1, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(unemp_000, col= "red"); lines(unemp_bs1, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_000, col= "red"); lines(ur_ds_bs1, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(ur_ds_01, col= "red"); lines(ur_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part
```

```{r}
plot(part_07b, col= "red"); lines(part_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_07b, col= "red"); lines(ur_ds_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```
